Robust calibration of numerical models based on relative regret

### 2020-01-21 article.tex
Figures scaling

@@

\begin{figure*}[!ht]
  \centering
  \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
  \caption{The left column concerns $\JBH$, while the right one deals with $\JBHS$. Contours of both functions are plotted on the top, and curves of  $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are shown on the bottom (respective scales are not displayed). Estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line.}
\label{fig:branin_moments}
\end{figure*}
%\clearpage % Pour lisibilité dans le preview

@@

Similarly, estimations of $\hatkmpe$ are depicted on Figure~\ref{fig:contours}. The top row shows the contours of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
The bottom row presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture, calculated with the EM algorithm. The number of Gaussians has been fixed to 3, a guess based on the general shape of the histogram. Respective estimations of $\hatkmpe$ are also depicted using dashed lines. 
\begin{figure}[!h]
  \centering
  \includegraphics[width=12cm]{Figures/branin_side_66.pdf}
  \caption{Top Left:  $\JBH$ along with conditional minimisers in red. Bottom left: Estimated densities using KDE and EM algorithm and the histogram. The dashed lines indicate the MPE found using those methods. Right: Same quantities with $\JBHS$.}
\label{fig:contours}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=12cm]{Figures/relaxation_tuto.pdf}
\caption{Principle of the relaxation of the constraint on $\JBH$, and illustration of $R_\alpha(\mathbf{k})$. Top plots: Computation of the conditional minimisers $\mathbf{k}^*(\mathbf{u})$. Top right plot: the set $(\mathbf{k}^*(\mathbf{u}),\mathbf{u})$ of conditional minimisers is represented in red. On the bottom left plot, for a relaxation $\alpha=1.5$, and $\mathbf{u}=3$, the acceptable $\mathbf{k}$ are in cyan, while the non-acceptable ones are in orange, while the frontier $\{(\mathbf{k}^*(\mathbf{u}),\mathbf{u}) \mid J^*(\mathbf{u}) = J(\mathbf{k},\mathbf{U}=\mathbf{u})\}$ is in yellow. On the bottom right plot, the set $R_{\alpha}(\mathbf{k})$ for $\alpha=1.5$ and $\mathbf{k}=1.5$ is in green.}
\label{fig:relax_tuto}
\end{figure*}

@@

The choice of the relaxation constant $\alpha$ can be made to ensure the existence of a parameter that is ``acceptable'' with a certain probability.
For instance, given that $J>0$, $\Gamma_{\alpha}(\mathbf{k})$ is increasing with respect to $\alpha$ for any $\mathbf{k}\in\Kspace$. We can then focus on the smallest value of $\alpha$ such that $\Gamma_\alpha$ reaches a certain level of confidence $p\in[0,1]$. This leads to the definition of $\checkap$
\begin{align}
  \checkap &= \inf\left\{ \alpha\geq 1 \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\} \nonumber \\
   &= \inf \left\{ \alpha \geq 1 \mid \max_{\mathbf{k}\in\Kspace} \Gamma_{\alpha}(\mathbf{k}) \geq p \right\}   \label{eq:def_alpha_check}
\end{align}
that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$.
$\{\mathbf{k}_p \text{ for } p \in [0;1] \}$ defines the relative-regret family of robust estimators (\RRE).
This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}). For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$ for $\JBHS$. By definition, the associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$. We can see that changing the level $p$ shifts the maximiser of $\Gamma_{\alpha_p}$, and that for small $\alpha$, $\Gamma_{\alpha}(\mathbf{k}_1)$ is also very small. This indicates that $\mathbf{k}_1$ is located quite far from the conditional minimisers, and arise as a compromise when the relaxation is large enough.

\begin{figure}[!ht]
\centering
\includegraphics[width = 0.7\textwidth]{Figures/illu_alpha_p.pdf}
\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$}
\label{fig:illu_alpha_p}
\end{figure}

@@

This alternative definition of $\checka_1$ is useful to estimate it quickly whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$. From Eq.~\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio $\frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})}$. Therefore it may suffer from the same pitfall as the worst-case approach. As mentioned in the introduction, this is not suited for random variable with unbounded support as it may return over-conservative solution, provided that a solution exists in the first place.

$\checkap$ can be an indicator of the robustness of $\checkkp$.  
A high value of $\checka_1$ corresponds to a high ratio $\frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$. In that sense, $J(\checkk_1,\mathbf{U}=\mathbf{u})$ may be possibly very high.
More generally, for a fixed level of confidence $p$, $\checkap$ is the slackness needed to be able to reach the probability $p$. % So, in addition to the value of the estimate $\checkkp$, we have an indicator of the robustness associated.
We can then see that it is sensible to study jointly $p$, $\checkap$ and $\checkkp$.

@@

% \victor{chapeau car ici je parle de l'estimation en pratique}
Also, choosing $p=1$ is possible only if the sample space of $\mathbf{U}$ is bounded. An illustration of this flaw appears in the following simple problem:
\begin{align*}
  \label{eq:Jinfinite}
  \Kspace &= \Uspace = [0,\,+\infty[ \\
  J(\mathbf{k},\mathbf{U}=\mathbf{u}) &= \mathbf{u}(\mathbf{k}-\mathbf{u})^2 + 1 \\
  \mathbf{k}^*(\mathbf{u}) &= \mathbf{u} \\
  J^*(\mathbf{u}) &= 1
\end{align*}
In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} \frac{J(\mathbf{k},\mathbf{U}=\mathbf{u})}{J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.

@@

\begin{figure*}[!ht]
  \centering
\includegraphics[width=12cm]{Figures/branin_side_66_relax_gamma_both.pdf}
\caption{Top: $\JBH$ and $\JBHS$ contours. The thick yellow lines are the boundaries of the acceptable region defined for $\hat{\checka}_1$, the thick orange are for $\alpha=1.5$. The red dashed line is the estimation $\hat{\checkk}_1$. Bottom: $\hat{\Gamma}_{\alpha}$ for $\alpha = 1.5$ and $\alpha=\hat{\checka}_1$, and estimated density of the minimisers.}
\label{fig:contour_alpha}
\end{figure*}

@@

 \begin{figure}[!ht]
   \centering
\includegraphics[width=0.8\textwidth]{Figures/alpha_p_BH.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBH$. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BH}
\end{figure}

@@

% \begin{table*}[!ht]
% \centering
% \caption{Estimation performed for $\JBH$, sorted by value}
% \label{tab:recap_estimates_branin}
% \begin{tabular}{lr}
% \toprule
% Estimate & Value \\ \midrule
% $\hatkvar$ & 1.371 \\ 
% $\kest_p,~p=1$ & 1.557 \\ 
% $\hatkmean$ & 1.587 \\ 
%   $\hatkmpe$ & 1.628 \\
%   $\kest_{\mathrm{ratio}},~\hat{p}_{\mathrm{ratio}}=0.654$ & 1.637 \\
% $\kest_p,~p=0.95$ & 1.672 \\ \bottomrule
% \end{tabular}
% \end{table*}
\begin{table*}[!h]
  \centering
\caption{Estimation performed for $\JBH$, sorted by value}
\begin{tabular}{lr}
  \toprule
Estimate & Value \\ \midrule
$\hatkvar$ & 1.371 \\ 
$\kest_{p},~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
$\kest_{\mathrm{MPE}}$ & 1.628 \\ 
$\kest_{\mathrm{ratio}},~\hat{p}_{\mathrm{ratio}}=0.654$ & 1.637 \\ 
$\kest_p,~p=0.90$ & 1.797 \\  \bottomrule
\end{tabular}
\label{tab:recap_estimates_branin}
\end{table*}
Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions $\mathbf{u} \mapsto J(\kest,\mathbf{U}=\mathbf{u})$, that we will call ``profiles of $\kest$''. Those profiles are well suited for the representation of the cost function for an estimate $\kest$ fixed as the uncertain variable is modelled with a 1D uniform random variable.

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=.8\textwidth]{Figures/profile_BH.pdf}
\caption{Profiles of the different estimates for $\JBH$, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The profiles of $\kest_{\mathrm{MPE}}$ and $\kest_{\mathrm{ratio}}$ coincide in this case}
\label{fig:profiles_branin}
\end{figure*}

@@

\begin{figure}[!h]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/alpha_p_BHs.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBHS$. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BHs}
\end{figure}

@@

\begin{table*}[!h]
\centering
\caption{Estimations performed for $\JBHS$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \toprule
Estimate & Value \\ \midrule
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{ratio}},~ \hat{p}_{\mathrm{ratio}}=0.766$ & 1.537 \\ 
$\hatkmean$ & 1.752 \\ 
$\hatkvar$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/profile_BHs.pdf}
\caption{Profiles of the different estimates for $\JBHS$. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$}
\label{fig:profiles_branin_switch}
\end{figure*}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=.9\textwidth]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{U}=\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.9\textwidth]{Figures/alpha_SWE}
  \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio, for the shallow water problem}
\label{fig:alpha_p_SWE}
\end{figure}

@@

\begin{table*}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria, for the shallow water problem}
\begin{tabular}{lr} \toprule
Estimate & Value \\ \midrule
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hatkp,~p=1$ & 0.423 \\ 
$\hatkp,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hatkp,~p=0.80$ & 0.505 \\ 
$\hatkp,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \bottomrule
\end{tabular}
\label{tab:recap_estimates_metaSWE}
\end{table*}
Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
\begin{figure}[!h]
  \centering
  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
  \caption{Profiles for the calibration problem, for the shallow water case}
\label{fig:profiles_swe}
\end{figure}
We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$. When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$, so more than half of the time. % As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.

% The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model.
We are now going to compare how well some of those calibrated values compare in a forecast context.
\subsection{Assessing the quality of the forecast of the calibrated model}
For the calibration, the model has been integrated on a time-period $[0, T]$, called assimilation window, and have been compared with the observation of the sea water height on the same time-period.
We now want to compare the quality of the different forecasts originating from different calibrated bottom frictions.
Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$: the forecast window.

@@

\begin{figure*}[!h]
\centering
\includegraphics[width=.9\textwidth]{Figures/L2_full_rel.pdf}
\caption{Squared forecast error for the shallow water case, depending on the calibrated parameter. The left figure shows the squared error time-averaged as a function of the spatial coordinate $x$, while the right barplot shows the relative change of the mean forecast error, averaged over time and space, taken w.r.t.\ to the best attained performance for $\mathbf{k}^*(0.7)$}
\label{fig:forecast_squared_error}
\end{figure*}

@@

\subsubsection{Continuous Ranked Probability Score}
Given the random variables $\mathcal{M}_{\mathrm{pred}}(\kest, \mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$, representing the probabilistic forecast and the probabilistic observations, we can define the cumulative distribution functions (CDF) $F_{\mathrm{pred}}(\cdot, \kest)$ and $F^o_{\mathrm{pred}}(\cdot)$
The Continuous ranked probability score (CRPS) measures the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observations $F_{\mathrm{pred}}^o$. 
\begin{equation}
\label{eq:def_crps}
\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(\xi,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}\xi
\end{equation}

\begin{figure}[!h]
  \centering
  \includegraphics[width=.9\textwidth]{Figures/CRPS_full_rel}
  \caption{CRPS computed for different calibrated parameters for the shallow water case. The left figure shows the CRPS time-averaged as a function of the spatial coordinate $x$, and the right figure shows the relative change of the CRPS averaged over time and space, taken with respect to the best attained CRPS for $\mathbf{k}^*(0.7)$}
\label{fig:forecast_crps}
\end{figure}

>>>>

\newlength{\minisize}
\setlength{\minisize}{3cm}
\newlength{\singlecolumnsize}
\setlength{\singlecolumnsize}{9cm}
\newlength{\onehalfcolumn}
\setlength{\onehalfcolumn}{14cm}
\newlength{\fullwidth}
\setlength{\fullwidth}{19cm}

@@

\begin{figure*}[!ht]
  \centering
  \includegraphics[width=\singlecolumnsize]{Figures/branin_side_moments_noscale.pdf}
  \caption{The left column concerns $\JBH$, while the right one deals with $\JBHS$. Contours of both functions are plotted on the top, and curves of  $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are shown on the bottom (respective scales are not displayed). Estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line.}
\label{fig:branin_moments}
\end{figure*}
%\clearpage % Pour lisibilité dans le preview

@@

Similarly, estimations of $\hatkmpe$ are depicted on Figure~\ref{fig:contours}. The top row shows the contours of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
The bottom row presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture, calculated with the EM algorithm. The number of Gaussians has been fixed to 3, a guess based on the general shape of the histogram. Respective estimations of $\hatkmpe$ are also depicted using dashed lines. 
\begin{figure}[!h]
  \centering
  \includegraphics[width=\singlecolumnsize]{Figures/branin_side_66.pdf}
  \caption{Top Left:  $\JBH$ along with conditional minimisers in red. Bottom left: Estimated densities using KDE and EM algorithm and the histogram. The dashed lines indicate the MPE found using those methods. Right: Same quantities with $\JBHS$.}
\label{fig:contours}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\onehalfcolumn]{Figures/relaxation_tuto.pdf}
\caption{Principle of the relaxation of the constraint on $\JBH$, and illustration of $R_\alpha(\mathbf{k})$. Top plots: Computation of the conditional minimisers $\mathbf{k}^*(\mathbf{u})$. Top right plot: the set $(\mathbf{k}^*(\mathbf{u}),\mathbf{u})$ of conditional minimisers is represented in red. On the bottom left plot, for a relaxation $\alpha=1.5$, and $\mathbf{u}=3$, the acceptable $\mathbf{k}$ are in cyan, while the non-acceptable ones are in orange, while the frontier $\{(\mathbf{k}^*(\mathbf{u}),\mathbf{u}) \mid J^*(\mathbf{u}) = J(\mathbf{k},\mathbf{U}=\mathbf{u})\}$ is in yellow. On the bottom right plot, the set $R_{\alpha}(\mathbf{k})$ for $\alpha=1.5$ and $\mathbf{k}=1.5$ is in green.}
\label{fig:relax_tuto}
\end{figure*}

@@

The choice of the relaxation constant $\alpha$ can be made to ensure the existence of a parameter that is ``acceptable'' with a certain probability.
For instance, given that $J>0$, $\Gamma_{\alpha}(\mathbf{k})$ is increasing with respect to $\alpha$ for any $\mathbf{k}\in\Kspace$. We can then focus on the smallest value of $\alpha$ such that $\Gamma_\alpha$ reaches a certain level of confidence $p\in[0,1]$. This leads to the definition of $\checkap$
\begin{align}
  \checkap &= \inf\left\{ \alpha\geq 1 \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\} \nonumber \\
   &= \inf \left\{ \alpha \geq 1 \mid \max_{\mathbf{k}\in\Kspace} \Gamma_{\alpha}(\mathbf{k}) \geq p \right\}   \label{eq:def_alpha_check}
\end{align}
that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$.
$\{\mathbf{k}_p \text{ for } p \in [0;1] \}$ defines the relative-regret family of robust estimators (\RRE).
This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ J(\mathbf{k},\mathbf{U}) / J^*(\mathbf{U})\}$, that is a measure of risk usually applied in the financial sector (see~\cite{rockafellar_deviation_2002}). For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$ for $\JBHS$. By definition, the associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$. We can see that changing the level $p$ shifts the maximiser of $\Gamma_{\alpha_p}$, and that for small $\alpha$, $\Gamma_{\alpha}(\mathbf{k}_1)$ is also very small. This indicates that $\mathbf{k}_1$ is located quite far from the conditional minimisers, and arise as a compromise when the relaxation is large enough.

\begin{figure}[!ht]
\centering
\includegraphics[width = \singlecolumnsize]{Figures/illu_alpha_p.pdf}
\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$}
\label{fig:illu_alpha_p}
\end{figure}

@@

This alternative definition of $\checka_1$ is useful to estimate it quickly whenever a grid over $\mathbb{K}\times\mathbb{U}$ has already been evaluated, thus avoiding multiple computations of $\Gamma_{\alpha}(\mathbf{k})$ until its maximum reaches $1$. From Eq.~\eqref{eq:upper_bound_alpha_check}, choosing a level of confidence equal to $1$ is then equivalent to looking for the worst-case scenario of the ratio ${J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})}$. Therefore it may suffer from the same pitfall as the worst-case approach. As mentioned in the introduction, this is not suited for random variable with unbounded support as it may return over-conservative solution, provided that a solution exists in the first place.

$\checkap$ can be an indicator of the robustness of $\checkkp$.  
A high value of $\checka_1$ corresponds to a high ratio ${J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})}$ for at least one particular $\mathbf{u}$. In that sense, $J(\checkk_1,\mathbf{U}=\mathbf{u})$ may be possibly very high.
More generally, for a fixed level of confidence $p$, $\checkap$ is the slackness needed to be able to reach the probability $p$. % So, in addition to the value of the estimate $\checkkp$, we have an indicator of the robustness associated.
We can then see that it is sensible to study jointly $p$, $\checkap$ and $\checkkp$.

@@

% \victor{chapeau car ici je parle de l'estimation en pratique}
Also, choosing $p=1$ is possible only if the sample space of $\mathbf{U}$ is bounded. An illustration of this flaw appears in the following simple problem:
\begin{align*}
  \label{eq:Jinfinite}
  \Kspace &= \Uspace = [0,\,+\infty[ \\
  J(\mathbf{k},\mathbf{U}=\mathbf{u}) &= \mathbf{u}(\mathbf{k}-\mathbf{u})^2 + 1 \\
  \mathbf{k}^*(\mathbf{u}) &= \mathbf{u} \\
  J^*(\mathbf{u}) &= 1
\end{align*}
In this case, for each $\mathbf{k}\in \Kspace$, $\lim_{\mathbf{u} \rightarrow + \infty} {J(\mathbf{k},\mathbf{U}=\mathbf{u})/J^*(\mathbf{u})} = + \infty$, so there is no $\mathbf{k}$ such that the ratio $J/J *$ can be bounded, hence $\alpha_1$ does not exist in this case.

@@

\begin{figure*}[!ht]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/branin_side_66_relax_gamma_both.pdf}
\caption{Top: $\JBH$ and $\JBHS$ contours. The thick yellow lines are the boundaries of the acceptable region defined for $\hat{\checka}_1$, the thick orange are for $\alpha=1.5$. The red dashed line is the estimation $\hat{\checkk}_1$. Bottom: $\hat{\Gamma}_{\alpha}$ for $\alpha = 1.5$ and $\alpha=\hat{\checka}_1$, and estimated density of the minimisers.}
\label{fig:contour_alpha}
\end{figure*}

@@

 \begin{figure}[!ht]
   \centering
\includegraphics[width=\onehalfcolumn]{Figures/alpha_p_BH.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBH$. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BH}
\end{figure}

@@

% \begin{table*}[!ht]
% \centering
% \caption{Estimation performed for $\JBH$, sorted by value}
% \label{tab:recap_estimates_branin}
% \begin{tabular}{lr}
% \toprule
% Estimate & Value \\ \midrule
% $\hatkvar$ & 1.371 \\ 
% $\kest_p,~p=1$ & 1.557 \\ 
% $\hatkmean$ & 1.587 \\ 
%   $\hatkmpe$ & 1.628 \\
%   $\kest_{\mathrm{ratio}},~\hat{p}_{\mathrm{ratio}}=0.654$ & 1.637 \\
% $\kest_p,~p=0.95$ & 1.672 \\ \bottomrule
% \end{tabular}
% \end{table*}
\begin{table}[!h]
  \centering
\caption{Estimation performed for $\JBH$, sorted by value}
\begin{tabular}{lr}
  \toprule
Estimate & Value \\ \midrule
$\hatkvar$ & 1.371 \\ 
$\kest_{p},~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
$\kest_{\mathrm{MPE}}$ & 1.628 \\ 
$\kest_{\mathrm{ratio}},~\hat{p}_{\mathrm{ratio}}=0.654$ & 1.637 \\ 
$\kest_p,~p=0.90$ & 1.797 \\  \bottomrule
\end{tabular}
\label{tab:recap_estimates_branin}
\end{table}
Practically speaking, in order to compare the effective values taken by the objective function given an estimate $\kest$ we are going to consider the functions $\mathbf{u} \mapsto J(\kest,\mathbf{U}=\mathbf{u})$, that we will call ``profiles of $\kest$''. Those profiles are well suited for the representation of the cost function for an estimate $\kest$ fixed as the uncertain variable is modelled with a 1D uniform random variable.

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/profile_BH.pdf}
\caption{Profiles of the different estimates for $\JBH$, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The profiles of $\kest_{\mathrm{MPE}}$ and $\kest_{\mathrm{ratio}}$ coincide in this case}
\label{fig:profiles_branin}
\end{figure*}

@@

\begin{figure}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/alpha_p_BHs.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBHS$. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BHs}
\end{figure}

@@

\begin{table}[!h]
\centering
\caption{Estimations performed for $\JBHS$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \toprule
Estimate & Value \\ \midrule
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{ratio}},~ \hat{p}_{\mathrm{ratio}}=0.766$ & 1.537 \\ 
$\hatkmean$ & 1.752 \\ 
$\hatkvar$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/profile_BHs.pdf}
\caption{Profiles of the different estimates for $\JBHS$. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$}
\label{fig:profiles_branin_switch}
\end{figure*}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=\singlecolumnsize]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{U}=\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/alpha_SWE}
  \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio, for the shallow water problem}
\label{fig:alpha_p_SWE}
\end{figure}

@@

\begin{table}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria, for the shallow water problem}
\begin{tabular}{lr} \toprule
Estimate & Value \\ \midrule
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hatkp,~p=1$ & 0.423 \\ 
$\hatkp,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hatkp,~p=0.80$ & 0.505 \\ 
$\hatkp,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \bottomrule
\end{tabular}
\label{tab:recap_estimates_metaSWE}
\end{table}

Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/profile_swe}
  \caption{Profiles for the calibration problem, for the shallow water case}
\label{fig:profiles_swe}
\end{figure}

We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$. When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$, so more than half of the time.
We are now going to compare how well some of those calibrated values compare in a forecast context.

\subsection{Assessing the quality of the forecast of the calibrated model}
For the calibration, the model has been integrated on a time-period $[0, T]$, called assimilation window, and have been compared with the observation of the sea water height on the same time-period.
We now want to compare the quality of the different forecasts originating from different calibrated bottom frictions.
Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$: the forecast window.

@@

\begin{figure*}[!h]
\centering
\includegraphics[width=\onehalfcolumn]{Figures/L2_full_rel.pdf}
\caption{Squared forecast error for the shallow water case, depending on the calibrated parameter. The left figure shows the squared error time-averaged as a function of the spatial coordinate $x$, while the right barplot shows the relative change of the mean forecast error, averaged over time and space, taken w.r.t.\ to the best attained performance for $\mathbf{k}^*(0.7)$}
\label{fig:forecast_squared_error}
\end{figure*}

@@

\subsubsection{Continuous Ranked Probability Score}
Given the random variables $\mathcal{M}_{\mathrm{pred}}(\kest, \mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$, representing the probabilistic forecast and the probabilistic observations, we can define the cumulative distribution functions (CDF) $F_{\mathrm{pred}}(\cdot, \kest)$ and $F^o_{\mathrm{pred}}(\cdot)$
The Continuous ranked probability score (CRPS) measures the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observations $F_{\mathrm{pred}}^o$. 
\begin{equation}
\label{eq:def_crps}
\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(\xi,\mathbf{k}) - F^o_{\mathrm{pred}}(\xi))^2 \,\mathrm{d}\xi
\end{equation}

\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/CRPS_full_rel}
  \caption{CRPS computed for different calibrated parameters for the shallow water case. The left figure shows the CRPS time-averaged as a function of the spatial coordinate $x$, and the right figure shows the relative change of the CRPS averaged over time and space, taken with respect to the best attained CRPS for $\mathbf{k}^*(0.7)$}
\label{fig:forecast_crps}
\end{figure}
